\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\usepackage{xparse}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\raggedright

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections.
\titlespacing{\section}{0pt}{5pt}{8pt} % Spacing around sections.


% Custom commands

\newcommand{\cvHeading}[3]{
\vspace{0.5mm}\item
    \begin{tabularx}{0.98\textwidth}[t]{X r}
        \textbf{#1} & \textit{\footnotesize{#2}} \\
        \textit{\footnotesize{#3}} &  {}\\
    \end{tabularx}
    \vspace{-2.4mm}
}

\newcommand{\cvProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.8\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\cvHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\cvHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\cvItemListStart}{\begin{justify}\begin{itemize}[leftmargin=1ex, rightmargin=2ex, noitemsep, labelsep=1.2mm, itemsep=0mm]\small}
\newcommand{\cvItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Custom commands.
\newcommand{\name}{Valentin Vignal}
\newcommand{\email}{val.vignal@live.fr}

\begin{document}
%----------HEADING-----------------

\par{\centering{\Huge Valentin \textsc{Vignal}}\bigskip\par}


\begin{tabularx}{\textwidth}{X X X}
  \href{mailto:\email}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\email}}                   & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +65-93356456}                                                  & \href{https://www.linkedin.com/in/valentin-vignal/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn}} \\
  \href{https://github.com/ValentinVignal}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub}} & \href{https://valentinvignal.github.io/portfolio/}{\raisebox{0.0\height}{\footnotesize \faGlobe}\ {Portfolio}}                                                                                                                     \\
\end{tabularx}


\section{\textbf{Personal Statement}}
Senior Full Stack Developer with 5 years
of expertise in Flutter, TypeScript, Svelte, and NestJS, committed to quality, continuous
learning, and honest, results-driven communication. Skilled in crafting
efficient, scalable solutions and fostering collaboration for excellence in a
dynamic environment.
I'm a member of the Flutter Github organization with contributor access and over 100
contributions.


\section{\textbf{Technology Stack}}

\begin{tabular}{@{}l l}
  Languages:           & Dart, TypeScript, Svelte, JavasScript, Rust, HTML+CSS, Python, Kotlin \\
  Frontend Frameworks: & Flutter, ReactJS, Svelte, SvelteKit                                   \\
  Backend Frameworks:  & NodeJS, Express, NestJS, GraphQL, TypeORM                             \\
  Platforms:           & macOS, Linux, Windows                                                 \\
  Databases:           & PostgreSQL, MySQL, SQLite, Firebase                                   \\
  Testing frameworks:  & Flutter test, Jest, Vitest, Playwright, Cypress                       \\
\end{tabular}

\section{\textbf{Experience}}
\subsection*{
  \begin{tabularx}{0.98\textwidth}[t]{@{}X r}
    Novade Solutions & \normalfont{\textit{\footnotesize{\href{https://www.novade.net/}{novade.net}}}} \\
  \end{tabularx}
}

\begin{tabular}{r|l}
  \footnotesize{Sep 2022 - Oct 2024} & Senior Full Stack Developer                \\
                                     & \textcolor{gray}{\footnotesize{Singapore}} \\
  \\
  \footnotesize{Jun 2019 - Aug 2022} & Software Developer                         \\
                                     & \textcolor{gray}{\footnotesize{Singapore}} \\
\end{tabular}


\subsubsection*{NovadeLite Project}

\textcolor{gray}{\small{NovadeLite (\textcolor{blue}{\href{https://lite.novade.net}{lite.novade.net}}) is a smart field management system for the building and construction
    industry. Keeping track of construction projects, assets, various kinds of forms, tasks, and managing people are some
    of the key features in this project.}}

\hspace{1pt}

\small \textbf{Tools and technologies}: {\footnotesize Flutter, Dart, Typescript, PostgreSQL, SQLite, GraphQL, NodeJS, NestJS, REST, Socket.io, TypeORM, Jest, Bitrise, Firebase, Sentry, Amplitude, Stripe, Git, Bash}.


\cvItemListStart
\item Worked as a full-stack developer (Frontend: Flutter, Backend: NodeJS, NestJS, GraphQL, REST, TypeORM, PostgreSQL).
\item Executed a comprehensive restructuring of the project's mono-repo architecture using Melos, resulting in a 50\% reduction in build, 10x reduction in code generation, and improved scalability.
\item Achieved a 40\% reduction in loading time by optimizing front-end development processes using Dart and Flutter.
\item Designed and developed a code generation tool for text key localization, effectively identifying and preventing 100\% of missing translation key bugs in production.
\item Integrated payment and subscription features, resulting in a 50\% increase in revenue within six months.
\item Implemented a company wide Quality Assurance (QA) process and Continuous Integration (CI) framework, leading to a 50\% decrease in bug reports and 30\% faster deployment cycles.
\item Established standardized protocols for code quality and consistency, resulting in a 40\% decrease in code review time and increase in developer productivity.
\item Overhauled the GraphQL API and PostgreSQL database, enhancing safety, relevance, and performance, resulting in a 15\% decrease of the project code size.
\item Code reviews and consultation on possible issues and edge cases reducing 10\% of possible regression issues.
\item Breaking down the user stories and estimations achieving near 100\% project goals on time.
\item Optimized Flutter's theme mechanism for consistent theming, and led end-to-end migration from Material Design 2 to Material Design 3.
\cvItemListEnd

\newpage


\section{\textbf{Voluntary Work}}


\subsection*{
  \begin{tabularx}{0.98\textwidth}[t]{@{}X r}
    Stack Overflow \normalfont{\footnotesize{(7.5k+ reputation)}} & \normalfont{\textit{\footnotesize{Sep 2019 - Present}}} \\
  \end{tabularx}
}
\vspace{-1em}
\normalfont{\textit{\footnotesize{\href{https://stackoverflow.com/users/12066144/valentin-vignal}{stackoverflow.com/users/12066144/valentin-vignal}}}}

\subsection*{
  \begin{tabularx}{0.98\textwidth}[t]{@{}X r}
    PyroNear & \normalfont{\textit{\footnotesize{Jan 2024 - Present}}} \\
  \end{tabularx}
}
\vspace{-1em}
\normalfont{\textit{\footnotesize{\href{https://pyronear.org//en/}{pyronear.org}}}}


\hspace{1em}

{\footnotesize\textcolor{gray}{ PyroNear is a complete fire risk management
    solution. It consists of an early wildfire detection algorithm, implemented on a
    microcomputer, connected to cameras positioned on high spots with a view on the
    forest. Our detectors communicate fire alerts to a database that is connected to
    a supervision platform for the fire department.}} \\

\hspace{1pt}

\small \textbf{Tools and technologies}: {\footnotesize TypeScript, ReactJS, Jest}
\cvItemListStart
\item Contributed to developing a front-end \textit{"crowdsourcer"} app for wildfire image uploads.
\item Implemented front-end tests using Jest for enhanced reliability.
\item Improved user experience by refactoring routing with React Router.
\cvItemListEnd


\section{\textbf{Open Source Contributions}}
\cvHeadingListStart
\cvHeading
{Flutter}{\href{https://flutter.dev/}{flutter.dev}}{
  I am a member of the Flutter Github organization with \href{https://github.com/flutter/flutter/pull/152361\#pullrequestreview-2201981291}{contributor access} to the repositories with over 100 contributions. My contributions to the flutter framework are mostly around the theme, testing and fixing memory leaks. \newline
  I am also a talker at the Flutter Singapore Meetup.
}


\cvHeading
{Go Router}{\href{https://pub.dev/packages/go_router}{go\_router}}{
  I led multiple major releases and made multiple contributions to go\_router and go\_router\_builder. Those where mostly about imperative routing and code generation.
}
\cvHeading{Riverpod}{\href{https://riverpod.dev/}{riverpod.dev}}{A reactive caching and data-binding framework. (Flutter)}
\cvHeading{Ferry}{\href{https://ferrygraphql.com/}{ferrygraphql.com}}{A simple, powerful GraphQL Client for Flutter and Dart. (Flutter)}
\cvHeading{Drift}{\href{https://drift.simonbinder.eu/}{drift.simonbinder.eu}}{Drift is a reactive persistence library for Flutter and Dart, built on top of SQLite. (Flutter, SQLite). My work was mostly around the code generator.}
\cvHeading{Nestjs-query}{\href{https://tripss.github.io/nestjs-query/}{nestjs-query}}{Nestjs-Query is collection of packages to make crud for graphql easier. (TypeScript, NestJS, GraphQL, PostgreSQL)}
\cvHeadingListEnd

\section{\textbf{Education}}
\cvHeadingListStart
\cvHeading
{Master degree in Computer Science}{Jan 2019 - Jun 2020}
{National University of Singapore, Singapore}
\cvHeading
{Master degree in Engineering}{Sep 2016 - Jun 2020}
{CentraleSupélec, France}
\cvHeadingListEnd


\section{\textbf{Personal Projects}}
\cvHeadingListStart
\cvHeading
{animated\_collection}
{\href{https://pub.dev/packages/animated_collection}{pub.dev}}
{A Flutter library with simple animated widgets and utilities methods to use with animations.}
\hspace{1em}

\hspace{1pt} \small \textbf{Tools and technologies}: {\footnotesize Dart, Flutter}

\cvHeading
{Padelistas}
{\href{https://padelistas-app.web.app/}{padelistas-app.web.app}, \href{https://github.com/ValentinVignal/padelistas}{Github}}
{A flutter application to organize padel games in Singapore.}
\hspace{1em}

\hspace{1pt} \small \textbf{Tools and technologies}: {\footnotesize Dart, Flutter, Firebase}

\cvHeading
{Dart Analyze}
{\href{https://github.com/marketplace/actions/dart-analyze}{dart-analyze}}
{A Github action that analyzes dart code by running \texttt{dart analyze} and \texttt{dart format}.}
\hspace{1em}

\hspace{1pt} \small \textbf{Tools and technologies}: {\footnotesize TypeScript, Dart, Flutter, Github Actions, Jest}

\cvHeading
{My Portfolio}
{\href{https://valentinvignal.github.io/portfolio}{valentinvignal.github.io/portfolio}}
{My portfolio website made with SvelteKit.}
\hspace{1em}

\hspace{1pt} \small \textbf{Tools and technologies}: {\footnotesize Svelte, SvelteKit, TypeScript, JavaScript, DaisyUI, TailwindCSS, Playwright, Vitest}

\cvHeading
{Chrome Markdown Emojis}
{\href{https://chromewebstore.google.com/detail/chrome-markdown-emojis/mojhbkjckfdaikbpfmmlfimchemiabln}{chromewebstore.google.com}}
{A TypeScript Google Chrome extension to insert emojis from their markdown code.}
\hspace{1em}

\hspace{1pt} \small \textbf{Tools and technologies}: {\footnotesize TypeScript, JavaScript, Chrome Extension, ReactJS, MaterialUI, Jest}

\cvHeadingListEnd
\end{document}
